Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-06-04 paper/introduction.tex
added neutron source description and geometry size

@@

where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
into two classes. Continuous parameters, including material thicknesses and
packing fraction, describe the geometry of a given reactor configuration. Discrete
categorical parameters then specify material selections, including
coolants, armours, and neutron multipliers. We set out to produce a fast TBR
function which takes these same input parameters and approximates the MC TBR
model with the greatest achievable regression performance.

>>>>

A point source with a Muir energy distribution \cite{openmcmuir} around 14.06MeV was used to approximate a DT plasma neutron source. 
The inner radius of the void region was 10m, the first wall thickness was 2.7cm and the blanket thickness was 2m.

@@

where T represents tritium and \isotope[7]{Li}, \isotope[6]{Li} are the more and
less common isotopes of lithium, respectively. The TBR is defined as the ratio between tritium generation in the breeding blanket and consumption in the reactor, whose input parameters in the-expensive MC model fall
into two classes. Continuous parameters, including material thicknesses and
packing fraction, describe the geometry of a given reactor configuration **TODO**add all the parameters here*****. Discrete
categorical parameters then specify material selections, including
coolants, armours, and neutron multipliers. We set out to produce a fast TBR
function which takes these same input parameters and approximates the MC TBR
model with the greatest achievable regression performance.
